Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-08-15 EMNLP-demo-paper/NLPVis-demo-paper.tex
add acknowledgement

\section*{Acknowledgments}
This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344.

>>>>

\section*{Acknowledgments}
This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344. This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, PIPER: ER26142 DE-SC0010498, and NVIDIA Corporation. This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375.
